Strings functions analysis

### 2022-08-24 article.tex
langs moved to results

    In order to investigate functions, we have to make a list of functions to be investigated. For this purpose, programming languages such as Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen. They were chosen based on parameters such as the number of questions on StackOverflow, the number of repositories on GitHub with 100+ stars, and the TIOBE Index; and they implement different paradigms (e.g. strict and non-strict typing in C++ and Python respectively). \hl{move langs to results, add some part of bench table}

@@

>>>>

    In order to investigate functions, we have to make a list of functions to be investigated. We chose N languages. They were chosen based on parameters such as the number of questions on StackOverflow, the number of repositories on GitHub with 100+ stars, and the TIOBE Index; and they implement different paradigms (e.g. strict and non-strict typing). \hl{add some part of bench table}

@@

    After considering the criteria, we chose 10 programming languages. Languages such as Java, Python, C++, Ruby, JavaScript, Go, C\#, Swift, PHP, Rust were chosen.
